Coherent optical association of a single molecule -- Supplemental material

### 2020-11-03 sm.tex
Update on Overleaf.

\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-1}
% \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}
\usepackage{footmisc}
\usepackage{braket}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\eff}{ef\! f}
\newcommand{\Na}{\mathrm{Na}}
\newcommand{\Cs}{\mathrm{Cs}}
\newcommand{\fxnote}[1]{{\textbf{[#1]}}}

\newcommand{\todo}[1]{}

\ifpdf
% Ensure reproducible output
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}
\hypersetup{
  pdfcreator={},
  pdfproducer={}
}
\fi

@@

\begin{document}
\title{Coherent optical association of a single molecule}
\author{Yichao~Yu}
\email{yichaoyu@g.harvard.edu}
\gradstudent
\author{Kenneth~Wang}
\gradstudent
\author{Jonathan~D.~Hood}
\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906}
\author{Lewis~R.~B.~Picard}
\gradstudent
\author{Jessie~T.~Zhang}
\gradstudent
\author{William~B.~Cairncross}
\harvardccb
\harvardphysics
\cua
\author{Jeremy~M.~Hutson}
\affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
\author{Till Rosenband}
\harvardphysics
\author{Kang-Kuen~Ni}
\email{ni@chemistry.harvard.edu}
\harvardccb
\harvardphysics
\cua

@@

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing the photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69\%$.
  The molecule has a binding energy of $770.20052(2) \mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power. We can state the tweezer power for where we measure it, but the transmission through the objective, etc. I believe is only estimated. (YYC: This is why the original number quoted was zero field. The current number is still for zero tweezer power), May also need to quote tweezer waist for power dependency}\todo{})
  with more than $60\%$ of the molecule created in the motional ground state.
  This technique does not rely on narrow excited state lines or Feshbach resonances
  and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

% Introduction

% 1. we want to have a diverse species to tailor to different applications including precision measurements and quantum engineering. 2. for the technique of associating atoms to form molecules, but so far all has been done with Feshbach association (before STIRAP), or in the case of Sr2, a narrow excited state. Previous work on near-threshold Raman transfer has been incoherent.
% (suggested referees: Florian Shreck and Immanual Bloch, Tanya, Deep Gupta, DeMille)

% Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum information and quantum simulation. (more detail to add here about applications?).

Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Yao2018, Wall2015, Sundar2018, wall2015realizing}, quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111,Segev2019}.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049, PhysRevLett.121.013202, PhysRevLett.120.123201}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020,He331}  have been achieved through the association of ultracold atoms.
% (any place to cite  molecular ion work?)
% Citations are not complete. Add them as you see fit.

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques that have been developed for atoms. Associating atoms into deeply-bound molecules is challenging because of the small wavefunction overlap between the free-atom and molecular state and the release of a large amount of binding energy. A two-step approach has been demonstrated to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance. The only exceptions are Sr$_2,$ where narrow linewidth ($\sim 20 ~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}. With these requirements, dimers between alkali atoms and non-magnetic atoms, or molecules involving atoms without narrow intercombination lines remain difficult to associate.
% These requirements limit the generality of previous association techniques.
% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly-bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}a. The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state. The resulting single molecule is in a well-defined internal quantum state and predominately in its motional ground state. A vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation. To further reduce the photon scattering and sensitivity to laser intensity noise, we choose the initial and final state to balance the two Rabi frequencies as much as possible. This system-independent approach can be used for creating new molecules atom-by-atom with full quantum state control.

\begin{figure*}
  \includegraphics[width=\textwidth]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematics of the optical transition from an atom pair to a weakly-bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $c^3\Sigma$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (b) Comparison between using a weakly-bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly-bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (c) Enhancement of short range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\mathrm{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser  with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate, $\Omega_R=\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_s$
% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
~\cite{Wineland2003}.
Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and therefore the scattering is predominantly from the target molecular state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally. Thus, the scattering is given by $ \Gamma_s=\Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power. Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.

Early experiments used weakly-bound excited states as the intermediate state
in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
However, for a complete picture, the many excited vibrational states in a molecular potential
as well as the excited atomic continuum need to be considered.
The total scattering rate and Raman Rabi rate become a sum of the scattering rates
and Raman Rabi rates over all possible intermediate states.
With these considerations, using a weakly-bound excited state as the intermeidate state
suffers from strong scattering of the nearby excited atomic continuum, resulting in large incoherence and loss to other molecular states.
This scattering is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold,
and thus can be made smaller by using deeply bound vibrational states as the intermediate level.

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency
and scattering rate at different detunings from the atomic threshold
taking into account of all states of
the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
and the continuum~\cite{Liu2017}.
The excited atomic continuum is particularly important for the target molecular state.
The sum of the squares of the wavefunction overlap
between the target weakly-bound molecular state
and all the excited molecular bound states is only about $0.02$,
suggesting that there is significant matrix element
between the target molecular state and the excited atomic continuum (See SM \todo{proper cite}).
This calculation shows that the ratio of the Raman Rabi rate to scattering rate
can be made larger for more deeply bound states compared to weakly-bound states
at a cost of a smaller Raman Rabi frequency
(Fig.~\ref{f-theory}b, full result in SM \todo{proper cite})
As a result, we choose the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state
to drive the Raman transition.

In addition to the intermediate state,
choosing an initial and a final state for a large $ \Omega_a/\Omega_m $ ratio
maximizes Raman Rabi coupling at a given detuning.
Furthermore, a larger ratio also relaxes the intensity stability requirement,
because this is also the ratio between the Raman Rabi coupling
and the AC Stark shift of the molecular state, $\Omega_m^2 / 2\Delta$
\footnote{There is an additional factor of 2, with both beams at equal power,
  to account for the Stark shift caused by both beams.}.
Due to the small size of the intermediate state wavefunction as compared to the trapped atoms,
the coupling $\Omega_a$ is approximately proportional to
the value of the relative atomic wavefunction at short distance
within the molecular potential.
To increase the amplitude within the molecular potential,
one can increase the external confinement of atom pairs.
Using a harmonic oscillator approximation,
the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $,
where $ \omega_{\text{trap}} $ is the trap frequency\cite{Mies2000}.
Alternatively, one can choose an atomic pair state with a large scattering length
(positive or negative).
For these states, the phase shift in the relative wavefunction
between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}c).
% The increase in the coupling is proportional to (quote/cite Olive's equation?).
For our system of Na and Cs atoms,
we choose a spin state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=3,m_F=3}_{\Cs}$ that has a large and negative scattering length of
$ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0$~\cite{Hood2019}.
All other stable spin combinations give smaller scattering lengths ($<~50~a_0$).
% We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\Cs}} = \ket{F=4,m_F=4}_{\Cs}, \ket{\downarrow_{\Cs}} = \ket{F=3,m_F=3}_{\Cs}, \ket{\uparrow_{\Na}} = \ket{F=2,m_F=2}_{\Na}, $ and $ \ket{\downarrow_{\Na}} = \ket{F=1,m_F=1}_{\Na}$. Among the stable spin combinations, $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\Na} \downarrow_{\Cs}} $ combination has a large and negative scattering length of $ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}.
For the target molecular state, we perform coupled-channel calculations
to identify the Rabi frequencies $\Omega_m$ to different weakly-bound spin states. The target's spin state is ideally similar to the initial spin state in order to minimize sensitivity to the B-field.
  % We find a target spin state predominantly in the initial spin state
  %that also has the advantage of having a reduced sensitivity
  %to laser intensity noise because of a larger %$\Omega_a/\Omega_b$ as compared to other states.
  %This reduces the intensity stability requirement to $5\%$
  %instead of $0.3\%$ which is typical for other states.
% In addition to the increased atomic coupling, $ \Omega_a $,
Coupled channel calculations show that this target molecular state also has reduced Rabi frequency, $ \Omega_m $,
with the intermediate state when compared to bound states of the other stable spin combinations, thus further increasing the $\Omega_a/\Omega_m$ ratio.
% $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
Using an initial $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination
results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003
with the other combinations, and thus relaxing the intensity stability requirement to the few percent level. % Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.
% Thus, we choose the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination.
% \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{fig2.pdf}
  \caption{
    (a) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to define the location of the
    atoms and molecule.
    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    (b) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
    When driving the Raman transition, the up leg power is smoothly ramped down and
    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
    with maximum Raman Rabi frequency when the up and down leg powers are equal.
    (c) Raman pulse time scan on resonance.
    A decaying Rabi oscillation can be observed proving the coherence of
    the Raman transfer process.
    Inset: Raman detuning scans at different times showing the resonance frequency.
    This is also fitted to a model of Raman transition
    with loss on the atom and molecule state and is used to determine
    both the Raman Rabi frequency and the loss rates.
    \label{f-raman}}
\end{figure}

%% Preparation
Experimentally, we first prepare two atoms in a well-defined external and internal quantum state using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}. In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into separate optical tweezers. The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom to be able to post select the experimental result on the initial loading condition. Raman sideband cooling is then applied to cool both atoms simultaneously into the 3-dimensional motional ground state of their optical tweezers. After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs} $ %and are merged into the same tweezer~\cite{Liu2019}. %The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $.
which has a small scattering length. The small two atom interaction allows the merging of the two atoms to be done with minimum pertubation so that they remain in the motional ground state.

% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 \mathrm{kHz}$ interaction shift~\cite{Hood2019}.  %using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\Cs}}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
This spin flip selectively transfers atoms in the relative motion ground state, removing any initial hot atom background from imperfect cooling \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}. For the experiment reported here, 31\% of our initial two atom population is successfully transferred.
% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}a). The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time. Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser. We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states. %to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
The pulse sequence is shown in Fig.~\ref{f-raman}b. %Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal.
% In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time.
After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
% In addition to reducing the number of laser beams during the Raman transition,

% found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency.
% The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037 \mathrm{nm}$ external cavity diode laser.
% by amplifying a $1037 \mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
% The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).  We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
% for a particular single photon detuning.

% in addition to the desired frequency. This increases the scattering rate due to coupling to other excited states.

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{fig3.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.199(9) \mathrm{ms}$
    measured from the Raman transition data.
    The oscillation in the survival is the result of the interference
    between the two Raman pulses with incomplete transfer.
    (b) Two-body atom lifetime of $5(1) \mathrm{ms}$
    in $15 \mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$ on a log-log scale,
    this is consistent with a two photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}

%% Experiment condition/resonance

We choose the tweezer frequency to be far detuned ($145 ~\mathrm{GHz}$) from the $v' = 0$ line, and guided by coupled channel calculations,
we locate the Raman resonance for the atom to molecule transition at
$770.57150(9) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}c inset)
with $15 ~\mathrm{mW}$ tweezer power.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$.
% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step,
so successful transfer of the atoms to the molecular state will be detected as loss.
We observed a Fourier limited linewidth which is evidence of a coherent transfer.
In order to verify the coherence of the transfer directly,
we fix the two photon detuning on resonance and scan the pulse time.
Fig.~\ref{f-raman}c shows the observed coherent Rabi oscillation between the atomic and molecular states.
Fitting the data with a decaying Rabi oscillation suggests that
$69\%$ of initial ground state atoms are transferred into the molecular state.
This transfer efficiency is mainly limited by the molecular lifetime
which can be measured directly by preparing the molecule with a $\pi $ pulse
and then using a second $\pi$ pulse to dissociate the molecule back to atoms
after a variable wait time (Fig.~\ref{f-lifetime}a).
The result shows a molecular lifetime of $0.199(9) \mathrm{ms}$
consistent with the decay of Rabi oscillation.
We obtain the Raman Rabi frequency by fitting our measurements to a model
that includes a Raman Rabi frequency and
a finite lifetime for the molecular state (Fig.~\ref{f-raman}c and inset).
We account for the effect of atomic state loss by measuring the one and
two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}b)
without turning on the second frequency.
The fit shows that we have a Raman Rabi frequency of $2\pi\times3.28(4) ~\mathrm{kHz}$.

The efficiency of the transfer is lower than expected from theory and arises from the ratio of the molecule scattering rate to the Rabi frequency being 10 times larger than predicted.
Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state,
it can be either due to a high ratio of $\Omega_m / \Omega_a$ or a large $\Gamma_e$.
Additionally, coupling to other excited states can also add an offset to
both the Raman Rabi frequency and the scattering rate
which can affect the scattering rate to Rabi frequency ratio.

In order to verify whether any one of these known sources are the origin of the discrepancy,
we measured the properties of the Raman resonance as a function of the tweezer power and single photon frequency.
These dependencies allow us to experimentally determine the matrix elements,
$ \Omega_a $, $\Omega_m $ and how much of the scattering, Stark shift,
or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.

First we look at the change in resonance frequency.
As a function of the tweezer power,
we observe the expected linear dependency on the resonance frequency
caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}a).
When we vary the tweezer frequency around the $v'=0$ intermediate state,
we can further observe a $1/\Delta$ component
and a constant background in the experimentally explored region.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is due to the coupling between the molecular state
and the $v'=0$ intermediate state.
From this measurement, we can extract a $\Omega_m$ of
$2\pi\times36.16(2) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or
$2\pi\times140.06(8) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
This number is close to the value of
$2\pi\times27 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}

>>>>

\documentclass[aps,secnumarabic,amsmath,amssymb,superscriptaddress]{revtex4}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}
\usepackage{listings}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\dispqlaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\eff}{ef\! f}

@@

% Add S1 to bibliography
\bibliographystyle{apsrev4-2}
\renewcommand*{\citenumfont}[1]{S#1}
\renewcommand*{\bibnumfmt}[1]{[S#1]}

%Add S to labels
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}%
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}%
\renewcommand{\thepage}{S\arabic{page}}  
\renewcommand{\thesection}{S\arabic{section}}   
\renewcommand{\theequation}{S.\arabic{equation}}

\begin{document}
\title{Coherent optical association of a single molecule -- Supplemental material}
\author{Yichao~Yu}
\email{yichaoyu@g.harvard.edu}
\gradstudent
\author{Kenneth~Wang}
\gradstudent
\author{Jonathan~D.~Hood}
\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906}
\author{Lewis~R.~B.~Picard}
\gradstudent
\author{Jessie~T.~Zhang}
\gradstudent
\author{William~B.~Cairncross}
\harvardccb
\harvardphysics
\cua
\author{Jeremy~M.~Hutson}
\affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
\author{Till Rosenband}
\harvardphysics
\author{Kang-Kuen~Ni}
\email{ni@chemistry.harvard.edu}
\harvardccb
\harvardphysics
\cua

@@

@@

\section{3 Level Raman Transfer with Cross Coupling}

Our Raman transfer scheme differs from typical Raman transfers, for instance between hyperfine states in atoms, in two key ways.

Test Reference\cite{Liu2019}

\bibliography{master-ref}
\end{document}
